Online Multiclass Linear Classification with Bandit Feedback

### 2018-12-18 arxiv-version/main.tex
Fixes

\begin{proposition}[Properties of $S_{n,r}$ and $B_{n,r}$]
\label{proposition:properties-of-s-n-r}
For any integer $n \ge 0$ and $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$,
\begin{enumerate}
\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
\end{enumerate}
\end{proposition}

@@

To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-1}
note that \autoref{proposition:properties-of-s-n-r} implies that
\begin{align*}
|p(x)|
& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
& \ge |Q(x)| \cdot 2^{s(s+1)rm} e^{-4} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4}$)} \\
& \ge 4 |Q(x)| \cdot 2^{s^2rm} && \text{(since $e^{-4} \ge 1/2$ and $2^{rms} \ge 8$)} \\
& \ge 4 |Q(x)| \cdot (4m+1)^{s^2m/2} && \text{(since $r \ge 1 + \frac{1}{2} \log_2(4m+1)$)} \\
& \ge 2 |Q(x)| \cdot m^{s^2m/2} \; .
\end{align*}
It thus remains to prove that
\begin{align}
Q(x) & \ge \frac{1}{2} && \text{for all} \ x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
Q(x) & \le -\frac{1}{2} && \text{for all} \ x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
\end{align}

>>>>

\begin{proposition}[Properties of $S_{n,r}$ and $B_{n,r}$]
\label{proposition:properties-of-s-n-r}
Let $n,m$ be non-negative integers.
Let $r = 2 \left\lceil \frac{1}{4} \log_2(4m + 1) \right\rceil + 1$. Then,
\begin{enumerate}
\item If $z \in [1,2^n]$ then $S_{n,r}(z) \in [1,1+\frac{1}{2m}]$.
\item If $z \in [-2^n, -1]$ then $S_{n,r} \in [-1-\frac{1}{2m}, -1]$.
\item If $z \in [-1,1]$ then $|S_{n,r}(z)| \le 1$.
\item If $z \in [-2^n,2^n]$ then $B_{n,r}(z) \ge \left(1 - \frac{1}{4m+1} \right) 2^{n(n+1)r}$.
\end{enumerate}
\end{proposition}

@@

To prove parts 1 and 2 of \autoref{theorem:polynomial-approximation-1}
note that \autoref{proposition:properties-of-s-n-r} implies that
\begin{align*}
|p(x)|
& = |Q(x)| \prod_{j=1}^m B_{s,r} \left( \frac{\ip{v_j}{x}}{\gamma} \right) \\
& \ge |Q(x)| \left( 2^{s(s+1)r} \left( 1 - \frac{1}{4m+1} \right) \right)^m \\
& \ge |Q(x)| \cdot 2^{s(s+1)rm} e^{-4} && \text{(since $\left(1-\frac{1}{4m+1}\right)^m \ge e^{-4}$)} \\
& \ge 4 |Q(x)| \cdot 2^{s^2rm} && \text{(since $e^{-4} \ge 1/2$ and $2^{rms} \ge 8$)} \\
& \ge 4 |Q(x)| \cdot (4m+1)^{s^2m/2} && \text{(since $r \ge 1 + \frac{1}{2} \log_2(4m+1)$)} \\
& \ge 2 |Q(x)| \cdot m^{s^2m/2} \; .
\end{align*}
Since $p(x)$ and $Q(x)$ have the same sign, it remains to prove that
\begin{align}
\label{equation:rational-margin-1}
Q(x) & \ge \frac{1}{2} && \text{for all} \ x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\} \; , \\
\label{equation:rational-margin-2}
Q(x) & \le -\frac{1}{2} && \text{for all} \ x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\} \; .
\end{align}
Consider any $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$. Then,
$\frac{\ip{v_i}{x}}{\gamma} \in [1, \frac{1}{\gamma}]$.
By part 1 of \autoref{proposition:properties-of-s-n-r}, $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \in [1, 1 + \frac{1}{2m}]$
and in particular $S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \ge 1$.
Thus, $Q(x) = \left( \sum_{i=1}^m S_{s,r}\left(\frac{\ip{v_i}{x}}{\gamma}\right) \right) - (m - 1/2) \ge m - (m - 1/2) = 1/2$.

Consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$.
Observe that $\frac{\ip{v_i}{x}}{\gamma} \in [-\frac{1}{\gamma}, \frac{1}{\gamma}]$.
TODO
